Rice yield improvements through plant breeding are offset by inherent yield declines over time

### 2018-03-05 output/review_responses.tex

\textbf{Comment: So in summary, I am not sure you need Fig 1, you could put the data of
  Fig 2 in Table 2 and bring it to the front along with Fig S1, and I
  don’t think you need Fig 6. But consider how you use the word
  “erosion” and discuss more thoroughly what could be causing the yield
  declines in Fig S1, and whether there is evidence it is happening also
  outside of the RES at Biggs.}\\

\textbf{Response:} Figure 1 has been moved to supplemental material,
and figure S1 has been moved to the main body. See above regarding
putting the data from figure 2 in tabular format.\\

\subsubsection{Sticky note comments}

\textit{Note: as the reviewer points out, these comments are largely
  repeated from above. Hence, for many comments, please refer to our
  responses above.}\\

@@

\textbf{Response: } It is inappropriate for the reviewer, who above plainly
states that they do not understand the statistics, to make this
evaluation.\\

\textbf{Comment: Give sentence on location (latitudes) and area of rice in
  CA. Even a map of the rice areas , also showing location of RES}\\

\textbf{Well it went backwards for several yeasr, and then resumed
  going up but at a slower rate. Somethink happened in mid 1990s?}\\

\textbf{Response: } This is speculation, and not directly relevant to
this study.\\

@@

\textbf{Comment: agreed, but is there something which groups cvs with
  declines and ones without??}\\

\textbf{Response: } See response above.\\

\textbf{Comment: Actually its over the time between release of M 202
  and M 206, 20 years or about 0.6 t/ha.}\\

\textbf{Response: } Or, more exactly 0.56 t/ha (560 kg/ha), as we
state in the manuscript.\\

### 2018-03-05 output/breed_paper_revised.Rnw
Adds map.

\documentclass[12pt,]{elsarticle}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{longtable,booktabs}
\usepackage{comment}
\usepackage{graphicx,grffile, textcomp}
\usepackage{setspace}
\usepackage{etoolbox}
\usepackage{float}
\doublespacing
\usepackage{lineno}
\usepackage{lscape} %% Harvard
\bibliographystyle{model2-names}\biboptions{authoryear}
\pagenumbering{gobble}
%% For figure numbers in supplementary info
%% from http://bytesizebio.net/2013/03/11/adding-supplementary-tables-and-figures-in-latex/
\newcommand{\beginsupplement}{%
  \setcounter{table}{0}
  \renewcommand{\thetable}{S\arabic{table}}%
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{S\arabic{figure}}%
}

@@

The CCRRF Rice Experiment Station (RES) is located near Biggs, CA
(39.4648, -121.7342), and has been the central location for CCRRF's
efforts to develop improved rice cultivars adapted to CA since
1969. The California Statewide Variety Trials evaluate current and
promising cultivars at the RES and six to eight on-farm trials around
the state each year. To avoid potential complications due to site,
climate, and management differences at the farmer-managed trials
between years, we focused our investigation on the RES. The RES is
researcher-managed and plants the majority of the experimental plots
for the statewide program (approximately 3 to 4 times the number of
experimental plots compared to other on-farm locations). The climate
at the RES is Mediterranean, characterized by mild winters during
which most of the annual precipitation occurs (\Sexpr{18*24.5} to
\Sexpr{25*24.5} mm annually) and warm summers largely free of
precipitation events. Soils at the RES are classified as
Esquon-Neerdobe clays with roughly 2\% soil organic matter in the top
15cm~\citep{ssurgo}.

@@

>>>>

\documentclass[12pt,]{elsarticle}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{longtable,booktabs}
\usepackage{comment}
\usepackage{graphicx,grffile, textcomp}
\usepackage{setspace}
\usepackage{etoolbox}
\usepackage{float}
\doublespacing
\usepackage{lineno}
\usepackage{lscape} %% Harvard
\usepackage[shortcuts]{extdash}
\bibliographystyle{model2-names}\biboptions{authoryear}
\pagenumbering{gobble}
%% For figure numbers in supplementary info
%% from http://bytesizebio.net/2013/03/11/adding-supplementary-tables-and-figures-in-latex/
\newcommand{\beginsupplement}{%
  \setcounter{table}{0}
  \renewcommand{\thetable}{S\arabic{table}}%
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{S\arabic{figure}}%
}

@@

The CCRRF Rice Experiment Station (RES) is located near Biggs, CA
(39.4648, \==121.7342; Fig. \ref{fig:map}), and has been the central location for CCRRF's
efforts to develop improved rice cultivars adapted to CA since
1969. The California Statewide Variety Trials evaluate current and
promising cultivars at the RES and six to eight on-farm trials around
the state each year. To avoid potential complications due to site,
climate, and management differences at the farmer-managed trials
between years, we focused our investigation on the RES. The RES is
researcher-managed and plants the majority of the experimental plots
for the statewide program (approximately 3 to 4 times the number of
experimental plots compared to other on-farm locations). The climate
at the RES is Mediterranean, characterized by mild winters during
which most of the annual precipitation occurs (\Sexpr{18*24.5} to
\Sexpr{25*24.5} mm annually) and warm summers largely free of
precipitation events. Soils at the RES are classified as
Esquon-Neerdobe clays with roughly 2\% soil organic matter in the top
15cm~\citep{ssurgo}.

@@

\begin{figure}[H]
  \includegraphics[]{map.pdf}
  \caption{The locations of the Rice Experiment Station relative to
    rice harvested area in California, USA.}
  \label{fig:map}
\end{figure}
